\Large \bf \projtitle

### 2015-05-07 doc/paper/paper.tex
adding results subsections
basic eval description

% TODO

@@

>>>>

We tested \zbf on a simple site that loads one large 768KB image from a remote server.
In our tests, we compare page load times using both plain HTTP and \zbf in a range of
scenarios. Specifically, we varied two parameters: the number of seeding peers and the
number of leeching peers. A seeding peer is a peer that has the desired resource, which
in our tests, was the single image on the site. A leeching peer is a peer that desires the
resource, so must request it either from the central site host or from peers with the resource.
Our tests launched a certain number of seeding peers, then launched a number of
leeching peers, measuring the average load latency for the leeching peers. We compare
this latency data with the page load latency when the leeching peers must load the content from the
central site host.

\subsection{Simulating the "reddit effect"}

Due to limitations

\subsection{Testing infrastructure}

% TODO selenium & scala
% anish should probably do this section

\subsection{Results}

@@

There remains numerous optimizations that would make \zbf more performant
when used on a deployed, high-traffic site. We detail these potential optimization
in this section.
